\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-15 paper/sp.tex
table

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$
and uncertainty $\ssigma_m$ for every star $m$.
\tablename~\ref{tab:output} shows a snippet of this output, with the full output available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining the table to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \gaia\ Archive (\citealt{gaiaarchive}).
In order to use this output with \apogee\ radial velocities and element abundances, we recommend
joining the table to the \sdssiv\ Catalog on the \zmass\ ID (name).
\begin{table}
\caption{HOGG TBD: The generated spectrophotometric parallaxes.\label{tab:output}}
\end{table}

@@

\acknowledgements
It is a pleasure to thank
  Coryn Bailer-Jones (\acronym{MPIA}),
  Sven Buder (\acronym{MPIA}),
  Andy L. Jones,
  Daniel Michalik (\acronym{ESTEC}),
  Melissa Ness (Columbia),
  Joel Zinn (OSU),
  and the participants in the \acronym{MPIA} Milky Way Group Meeting
for help with this project.
This project was developed in part at the
2018 \acronym{NYC} Gaia Sprint, hosted by the Center for Computational Astrophysics of
the Flatiron Institute in New York City in 2018 June.

>>>>

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$
and uncertainty $\ssigma_m$ for every star $m$.
\tablename~\ref{tab:output} shows a snippet of this output, with the full output available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining the table to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \gaia\ Archive (\citealt{gaiaarchive}).
In order to use this output with \apogee\ radial velocities and element abundances, we recommend
joining the table to the \sdssiv\ Catalog on the \zmass\ ID (name).
\begin{table}
\caption{HOGG and ACE TBD: The generated spectrophotometric parallaxes.
This table is just a snippet; the full table is available online (HOGG HOW?)\label{tab:output}}
\end{table}

@@

\acknowledgements
It is a pleasure to thank
  Coryn Bailer-Jones (\acronym{MPIA}),
  Sven Buder (\acronym{MPIA}),
  Andy L. Jones,
  Daniel Michalik (\acronym{ESTEC}),
  Melissa Ness (Columbia),
  Joel Zinn (OSU),
  and the participants in the \acronym{MPIA} Milky Way Group Meeting
  and the \apogee\ Science Telecon,
for help with this project.
This project was developed in part at the
2018 \acronym{NYC} Gaia Sprint, hosted by the Center for Computational Astrophysics of
the Flatiron Institute in New York City in 2018 June.
